---
title: "Hello, Penguins!"
format: html
editor: visual
execute: 
  echo: true
---

# Introduction

## Data {.smaller}

For this analysis we'll use the `penguins` dataset from the [**palmerpenguins**](https://allisonhorst.github.io/palmerpenguins/) package.

```{r}
#| label: load-packages
#| message: false
#| include: false

library(tidyverse)
library(ggthemes)
library(palmerpenguins)
library(gt)
```

```{r}
glimpse(penguins)
```

## Species

@fig-bill-dims-species is a scatter plot of species of penguins.

```{r}
#| label: fig-bill-dims-species
#| fig-width: 5
#| fig-asp: 0.618
#| fig-alt: |
#|   A scatterplot of penguins' bill depth and length, colored by
#|   species of penguins. There is a relatively strong, linear
#|   association.
#| fig-cap: |
#|   A scatterplot of penguins' bill depth and length, colored by
#|   species of penguins.
#| code-line-numbers: "|9|10-11"
#| output-location: slide
#| echo: fenced

ggplot(
  penguins,
  aes(
    x = bill_length_mm, y = bill_depth_mm,
    color = species
  )
) +
  geom_point() +
  geom_smooth() +
  scale_color_colorblind() +
  theme(legend.position = "top") +
  labs(x = "Bill length (mm)", y = "Bill depth (mm)")
```

## Penguins {.smaller}

@tbl-penguins-top10 shows the first 10 penguins from the dataset.

```{r}
#| label: tbl-penguins-top10
#| tbl-cap: First 10 penguins.

penguins |> # <1>
  slice_head(n = 10) |> # <2>
  select(species, island, bill_length_mm, bill_depth_mm) |> # <3>
  gt() # <3>
```

1.  Start with the `penguins` data frame
2.  Then slice the top ten rows
3.  Select some variables and make a table with `gt()`

# Analysis

## Modeling results

Some modeling results go here...
